CONEM2024-0014 \\ AN EXACT METHOD FOR THE MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving text

The method applied in this work consists of identifying new optimization problems, and mathematically modeling as well as proposing a new solution methodology for the identified problems. The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, as cited in this article. The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.

>>>>

The method applied in this work consists of identifying new optimization problems, and mathematically modeling as well as proposing a new solution methodology for the identified problems. This work was developed following a practice-based learning approach, as described in the work of \cite{Fraga2022}. The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX software, as well as platforms for the development of group work, such as GitHub and Google Classroom. The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.
